\speculake: Hiding Malware in Speculative Execution

### 2018-08-08 paper/architecture.tex
shift disclaimer up

@@

In this section, we will describe the trigger program variant, and discuss how
input data can be used a speculative trigger in
Section~\ref{sec:spec-buffer-overflow}.

>>>>

In this subsection, we will describe the trigger program variant, and discuss how
input data can be used a speculative trigger in
Section~\ref{subsec:spec-buffer-overflow}.

@@
